---
title: "Stats 140SL Analysis"
author: "Cassandra Tai"
date: "11/30/2020"
output: html_document
---

## set working directory 
```{r}
setwd("C:\\Users\\cassa\\Documents\\UCLA\\Fourth Year\\Stats 140SL\\final project") #change it to your own!
```  

## load libraries
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
```


## Read in data
```{r}
data <- read.csv("return_data.csv", header = TRUE)
dim(data)
```

## Clean Data
```{r}
data <- data[!is.na(data$return_percent),]
data <- data[data$return_percent != 0,]
dim(data)
str(data)
head(data)

# baseline data
stock <- c("Amazon","Disney","Intel", "Tesla")
base<-data.frame(c("Amazon","Disney","Intel", "Tesla"), as.numeric(c(169,98,95,576)))
colnames(base) = c("stock","return_percent")
base
```


## finding means
### aggregate based on ma type and stock and table
```{r}
data_means <- data %>% group_by(stock, ma_type)%>% summarize(means = mean(return_percent)) %>% as.data.frame()
data_means
table_means <- spread(data_means, key=ma_type, value = means)
table_means
```

## groups by price_ma/sentiment_ma type regardless of price/sentiment windows
```{r}
method_type <- data %>% group_by(stock, method_type) %>% summarize(means = mean(return_percent))
method_ma_type <- data %>% group_by(stock, ma_type, method_type) %>% summarize(means = mean(return_percent))
method_type
method_ma_type
```

# hypothesis testing
## for reddit sentiment
```{r}
reddit.AMZ <- t.test(data[which(data$stock == "Amazon" & data$ma_type=="reddit"),"return_percent"]-base[1,2], alternative = "greater")
reddit.DIS <- t.test(data[which(data$stock == "Disney" & data$ma_type=="reddit"),"return_percent"]-base[2,2], alternative = "greater")
reddit.INT <- t.test(data[which(data$stock == "Intel" & data$ma_type=="reddit"),"return_percent"]-base[3,2], alternative = "greater")
reddit.TSL <- t.test(data[which(data$stock == "Tesla" & data$ma_type=="reddit"),"return_percent"]-base[4,2], alternative = "greater")

reddit.AMZ
reddit.DIS
reddit.INT
reddit.TSL
```

## now for twitter sentiment
```{r}
twitter.AMZ <- t.test(data[which(data$stock == "Amazon" & data$ma_type=="twitter"),"return_percent"]-base[1,2], alternative = "greater")
twitter.DIS <- t.test(data[which(data$stock == "Disney" & data$ma_type=="twitter"),"return_percent"]-base[2,2], alternative = "greater")
twitter.INT <- t.test(data[which(data$stock == "Intel" & data$ma_type=="twitter"),"return_percent"]-base[3,2], alternative = "greater")
twitter.TSL <- t.test(data[which(data$stock == "Tesla" & data$ma_type=="twitter"),"return_percent"]-base[4,2], alternative = "greater")

twitter.AMZ
twitter.DIS
twitter.INT
twitter.TSL
```

## now for price
```{r}
price.AMZ <- t.test(data[which(data$stock == "Amazon" & data$ma_type=="price"),"return_percent"]-base[1,2], alternative = "greater")
price.DIS <- t.test(data[which(data$stock == "Disney" & data$ma_type=="price"),"return_percent"]-base[2,2], alternative = "greater")
price.INT <- t.test(data[which(data$stock == "Intel" & data$ma_type=="price"),"return_percent"]-base[3,2], alternative = "greater")
price.TSL <- t.test(data[which(data$stock == "Tesla" & data$ma_type=="price"),"return_percent"]-base[4,2], alternative = "greater")

price.AMZ
price.DIS
price.INT
price.TSL
```


# Make table for p-values
```{r}
p.vals <- data.frame(stock = c("Amazon","Disney","Intel", "Tesla"),
           reddit.pval = round(c(reddit.AMZ$p.value, reddit.DIS$p.value, reddit.INT$p.value, reddit.TSL$p.value),4),
           twitter.pval = round(c(twitter.AMZ$p.value, twitter.DIS$p.value, twitter.INT$p.value, twitter.TSL$p.value),4),
           price.pval = round(c(price.AMZ$p.value, price.DIS$p.value, price.INT$p.value, price.TSL$p.value),4))
p.vals
```

# Make table of means for graph
```{r}
df <- data_means %>% filter(stock %in% c("Disney", "Intel") & ma_type %in% c("reddit"))
df <- rbind(df, c(stock = "Disney", ma_type = "base", means = base$return_percent[2]))
df <- rbind(df, c(stock = "Intel", ma_type = "base", means = base$return_percent[3]))
colnames(df) = c("Stock", "Method", "PercentReturn")
#df
df$Method <- as.character(df$Method)
df$Method[1:2] <- "Reddit"
df$Method[3:4] <- "Baseline"
df$Method <- factor(df$Method)
#df
df$PercentReturn <- as.numeric(df$PercentReturn)
df$PercentReturn <- df$PercentReturn-100
df
```


# Make a bargraph
```{r}
ggplot(data = df, aes(fill = Method, x = Stock, y = PercentReturn)) + 
  geom_bar(position = position_dodge(), stat= "identity",color="black") +
  ylab("Percentage Return") + 
  ggtitle("Using Reddit Sentiment to Increase Stock Return Investments") + 
  scale_fill_manual(values = c("red","#6aa84f"))+
  theme_minimal() + 
  #scale_fill_brewer(palette="Blues") + 
  theme(plot.title = element_text(size=18,color = "white", face = "bold"), 
        axis.title.x = element_text(size=17,color = "white", face = "bold"), 
        axis.title.y = element_text(size=17,color = "white", face = "bold"),
        axis.title.y.right = element_text(color = "#2774ae"),
        axis.text.y.right = element_text(color = "#2774ae"),
        axis.text.x = element_text(size=14,color = "white"), axis.text.y = element_text(size=14,color = "white"), 
        #axis.ticks = element_text(color = "white"),
        legend.title=element_text(size=14,color = "white"), 
        legend.text=element_text(size=13,color = "white"),
        plot.background= element_rect("#2774ae"),
        legend.position="top") +
  scale_y_continuous(
    sec.axis = sec_axis(~ . + 100, name = "Percentage Return"), position = "right")
```

This one has twitter
```{r}
#make the dataframe for graph
df <- data_means %>% filter(stock %in% c("Disney", "Intel") & ma_type %in% c("reddit","twitter"))
df
df$Method <- as.character(df$Method)
df <- rbind(df, c(stock = "Disney", ma_type = "base", means = base$return_percent[2]))
df <- rbind(df, c(stock = "Intel", ma_type = "base", means = base$return_percent[3]))
colnames(df) = c("Stock", "Method", "PercentReturn")
df$Method <- factor(df$Method)

df$PercentReturn <- as.numeric(df$PercentReturn)
df$PercentReturn <- df$PercentReturn-100
df

ggplot(data = df, aes(fill = Method, x = Stock, y = PercentReturn)) + 
  geom_bar(position = position_dodge(), stat= "identity",color="black") +
  ylab("Percentage Return") + 
  ggtitle("Using Reddit Sentiment to Increase Stock Return Investments") + 
  scale_fill_manual(values = c("red","#6aa84f","blue"))+
  theme_minimal() + 
  #scale_fill_brewer(palette="Blues") + 
  theme(plot.title = element_text(size=18,color = "white", face = "bold"), 
        axis.title.x = element_text(size=17,color = "white", face = "bold"), 
        axis.title.y = element_text(size=17,color = "white", face = "bold"),
        axis.title.y.right = element_text(color = "#2774ae"),
        axis.text.y.right = element_text(color = "#2774ae"),
        axis.text.x = element_text(size=14,color = "white"), axis.text.y = element_text(size=14,color = "white"), 
        #axis.ticks = element_text(color = "white"),
        legend.title=element_text(size=14,color = "white"), 
        legend.text=element_text(size=13,color = "white"),
        plot.background= element_rect("#2774ae"),
        legend.position="top") +
  scale_y_continuous(
    sec.axis = sec_axis(~ . + 100, name = "Percentage Return"), position = "right")
```
